Programming Distributed Control Planes

### 2016-01-21 paper/compilation.tex
more edits

TODO

>>>>

Although every path through the product graph is a valid path in the topology, we typically do not want to consider loops when configuring a network. In particular, BGP's loop prevention mechanism (where an AS rejects any route for which it is already in the AS path), means that loops should never occur \footnote{Misconfigured aggregation can still lead to loops in some cases}. When analyzing the user policy for correctness and failure safety, it is often useful to avoid considering possibilities that cannot
